---
title: "Robustness to model misspecification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Robustness to model misspecification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
#robustness to model misspecification
```

```{r setup}
library(CoOPLBM)
library(pROC)
library(ggplot2)
library(reshape2)
library(aricode)
library(gridExtra)
library(sbm)
```

To show the robustness of the developed algorithm for CoOP-LBM, a series of examples is available on this page, where the settings are different from the one defined in the article. The criterion used to compare the quality of the estimation is the AUC of the probability of finding the missing links in $M$, and the ARI score of the estimated clustering with the true clustering.

```{r}
n1 = 100
n2 = 100
Q1 = 3
Q2 = 3
P =matrix(c(0.95,0.75,0.5,
                 0.75,0.5,0.5,
                 0.5,0.5,0.05),Q1,Q2)


alpha1 = c(1/3,1/3,1/3)
alpha2 = c(1/3,1/3,1/3)
G=50
```


# $N_{i,j}$ is a Gamma-Poisson mixture

In order to increase the variance of $N_{i,j}$, we will now have $N_{i,j}\sim\mathcal{P}(\nu_{i,j})$ where $\nu_{i,j}$ is a Gamma random variable of shape $G/p$ and scale $\lambda_i\mu_jp$ with $p$ any positive number. In this example we will take $p = 4$.

```{r}
result1 = data.frame(ARI_row_LBM=numeric(),
                    ARI_col_LBM=numeric(),
                    ARI_row_CoOP = numeric(),
                    ARI_col_CoOP = numeric(),
                    ARI_row_DCSBM = numeric(),
                    ARI_col_DCSBM = numeric(),
                    AUC_LBM = numeric(),
                    AUC_CoOP = numeric(),
                    AUC_DCSBM = numeric()
                   )
```


```{r simu1, cache = TRUE, message=FALSE, results='hide'}
for (k in 1:30){
simulation1=simulate_lbm(P,alpha1,alpha2,n1,n2)
M = simulation1$A
Z1 =simulation1$Z
Z2 =simulation1$W
lambda_i =rbeta(n1,0.3,1.5)
mu_j = rbeta(n2,0.3,1.5)
lambda_i = lambda_i/max(lambda_i)
mu_j = mu_j/max(mu_j)
N0=rgamma(n=n1*n2,shape=G/4,scale=lambda_i%*%t(mu_j)*4)
N=matrix(rpois(n1*n2,N0),nrow=n1)
R = M*N

obsrow = rowSums(R)>0
obscol = colSums(R)>0
R_obs = R[obsrow,obscol]
M_obs = M[obsrow,obscol]
Z1_obs = Z1[obsrow]
Z2_obs = Z2[obscol]
V = 1*(R_obs>0)

cov_row = lapply(2:nrow(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[k,] = 1
  X
})
cov_col = lapply(2:ncol(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[,k] = 1
  X
})


try1=fit_unsupervised_LBM(V,exploOptions = list(plot=FALSE,verbosity=F))
try2=fit_unsupervised_CoOP_LBM(R_obs,exploOptions = list(plot=F,verbosity=F))
try3 = estimateBipartiteSBM(R_obs,model = "poisson",covariates = c(cov_row,cov_col),estimOptions = list(plot=F,verbosity=0,exploreMax = 10))

model1 = try1[[best_ICL(try1)]]
model2 = try2[[best_ICL(try2)]]
model3 = try3

proba_connect1 = model1$pi[model1$cluster1,model1$cluster2]
proba_connect2 = model2$connectivity_prob
proba_connect3 = 1-exp(-fitted(model3))



ARIL1=ARI(model1$cluster1,Z1_obs)
ARIC1=ARI(model1$cluster2,Z2_obs)

ARIL2=ARI(model2$cluster1,Z1_obs)
ARIC2=ARI(model2$cluster2,Z2_obs)

ARIL3=ARI(model3$memberships$row,Z1_obs)
ARIC3=ARI(model3$memberships$col,Z2_obs)

AUC_LBM  = auc(roc(M_obs[V==0],proba_connect1[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_CoOP = auc(roc(M_obs[V==0],proba_connect2[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_DCSBM = auc(roc(M_obs[V==0],proba_connect3[V==0],
                    direction="<",levels=levels(as.factor(c(0,1)))))
result1[nrow(result1)+1,] = c(ARIL1,ARIC1,ARIL2,ARIC2,ARIL3,ARIC3,AUC_LBM,AUC_CoOP,AUC_DCSBM)

}
```


```{r, warning = FALSE}

df1 = result1[c("ARI_row_LBM","ARI_row_CoOP","ARI_row_DCSBM")]
df1 = melt(df1)
p1 <- ggplot(df1, aes(y=value,fill=variable))+
  geom_boxplot() +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for row clustering")+ labs(y="ARI",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM"))+ guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))

df2 = result1[c("ARI_col_LBM","ARI_col_CoOP","ARI_col_DCSBM")]
df2 = melt(df2)
p2 <- ggplot(df2, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for column clustering")+ labs(y="",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))


grid.arrange(p1,p2,ncol=2)

```

```{r,warning=FALSE}
df3 = result1[c("AUC_LBM","AUC_CoOP","AUC_DCSBM")]

df3_long <- melt(df3)
p3 <- ggplot(df3_long, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("AUC for missing data")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+labs(y="AUC")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))
p3
```


# $\lambda$ and $\mu$ are structured in cluster independent from $Z^1$ and $Z^2$

In this situation, $\lambda$ and $\mu$ are also structured, this simulation is done to see if the structure of the sampling can perturb the estimation of network's structure.
```{r}
result2 = data.frame(ARI_row_LBM=numeric(),
                    ARI_col_LBM=numeric(),
                    ARI_row_CoOP = numeric(),
                    ARI_col_CoOP = numeric(),
                    ARI_row_DCSBM = numeric(),
                    ARI_col_DCSBM = numeric(),
                    AUC_LBM = numeric(),
                    AUC_CoOP = numeric(),
                    AUC_DCSBM = numeric()
                   )
```

```{r simu2 , cache=T, message=FALSE, results='hide'}
for (k in 1:30){
simulation1=simulate_lbm(P,alpha1,alpha2,n1,n2)
M = simulation1$A
Z1 =simulation1$Z
Z2 =simulation1$W
lambda_i =sample(c(0.01,0.25,0.5),size=100,replace=T,prob=c(0.5,0.4,0.1))
mu_j = sample(c(0.01,0.25,0.5),size=100,replace=T,prob=c(0.5,0.4,0.1))
lambda_i = lambda_i/max(lambda_i)
mu_j = mu_j/max(mu_j)
N0=lambda_i%*%t(mu_j)*G
N=matrix(rpois(n1*n2,N0),nrow=n1)
R = M*N

obsrow = rowSums(R)>0
obscol = colSums(R)>0
R_obs = R[obsrow,obscol]
M_obs = M[obsrow,obscol]
Z1_obs = Z1[obsrow]
Z2_obs = Z2[obscol]
V = 1*(R_obs>0)

cov_row = lapply(2:nrow(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[k,] = 1
  X
})
cov_col = lapply(2:ncol(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[,k] = 1
  X
})


try1=fit_unsupervised_LBM(V,exploOptions = list(plot=FALSE,verbosity=F))
try2=fit_unsupervised_CoOP_LBM(R_obs,exploOptions = list(plot=F,verbosity=F))
try3 = estimateBipartiteSBM(R_obs,model = "poisson",covariates = c(cov_row,cov_col),estimOptions = list(plot=F,verbosity=0,exploreMax = 10))

model1 = try1[[best_ICL(try1)]]
model2 = try2[[best_ICL(try2)]]
model3 = try3

proba_connect1 = model1$pi[model1$cluster1,model1$cluster2]
proba_connect2 = model2$connectivity_prob
proba_connect3 = 1-exp(-fitted(model3))



ARIL1=ARI(model1$cluster1,Z1_obs)
ARIC1=ARI(model1$cluster2,Z2_obs)

ARIL2=ARI(model2$cluster1,Z1_obs)
ARIC2=ARI(model2$cluster2,Z2_obs)

ARIL3=ARI(model3$memberships$row,Z1_obs)
ARIC3=ARI(model3$memberships$col,Z2_obs)

AUC_LBM  = auc(roc(M_obs[V==0],proba_connect1[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_CoOP = auc(roc(M_obs[V==0],proba_connect2[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_DCSBM = auc(roc(M_obs[V==0],proba_connect3[V==0],
                    direction="<",levels=levels(as.factor(c(0,1)))))
result2[nrow(result2)+1,] = c(ARIL1,ARIC1,ARIL2,ARIC2,ARIL3,ARIC3,AUC_LBM,AUC_CoOP,AUC_DCSBM)

}
```


```{r, warning = FALSE}

df1 = result2[c("ARI_row_LBM","ARI_row_CoOP","ARI_row_DCSBM")]
df1 = melt(df1)
p1 <- ggplot(df1, aes(y=value,fill=variable))+
  geom_boxplot() +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for row clustering")+ labs(y="ARI",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM"))+ guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))

df2 = result2[c("ARI_col_LBM","ARI_col_CoOP","ARI_col_DCSBM")]
df2 = melt(df2)
p2 <- ggplot(df2, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for column clustering")+ labs(y="",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))


grid.arrange(p1,p2,ncol=2)

```

```{r,warning=FALSE}
df3 = result2[c("AUC_LBM","AUC_CoOP","AUC_DCSBM")]

df3_long <- melt(df3)
p3 <- ggplot(df3_long, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("AUC for missing data")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+labs(y="AUC")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))
p3
```

# One line is over sampled compared to the other

In this situation, the model is the same as usual, but the parameter $G$ is changed for one line, which represent an over sampled species.

```{r}
result3 = data.frame(ARI_row_LBM=numeric(),
                    ARI_col_LBM=numeric(),
                    ARI_row_CoOP = numeric(),
                    ARI_col_CoOP = numeric(),
                    ARI_row_DCSBM = numeric(),
                    ARI_col_DCSBM = numeric(),
                    AUC_LBM = numeric(),
                    AUC_CoOP = numeric(),
                    AUC_DCSBM = numeric()
                   )
```

```{r  simu3 , cache=T, message=FALSE, results='hide'}
for (k in 1:30){
simulation1=simulate_lbm(P,alpha1,alpha2,n1,n2)
M = simulation1$A
Z1 =simulation1$Z
Z2 =simulation1$W
lambda_i =rbeta(n1,0.3,1.5)
mu_j = rbeta(n2,0.3,1.5)
lambda_i = lambda_i/max(lambda_i)
mu_j = mu_j/max(mu_j)
N0=lambda_i%*%t(mu_j)*G
N0[1,] = lambda_i[1] * mu_j * G * 6 
N=matrix(rpois(n1*n2,N0),nrow=n1)
R = M*N

obsrow = rowSums(R)>0
obscol = colSums(R)>0
R_obs = R[obsrow,obscol]
M_obs = M[obsrow,obscol]
Z1_obs = Z1[obsrow]
Z2_obs = Z2[obscol]
V = 1*(R_obs>0)

cov_row = lapply(2:nrow(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[k,] = 1
  X
})
cov_col = lapply(2:ncol(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[,k] = 1
  X
})


try1=fit_unsupervised_LBM(V,exploOptions = list(plot=FALSE,verbosity=F))
try2=fit_unsupervised_CoOP_LBM(R_obs,exploOptions = list(plot=F,verbosity=F))
try3 = estimateBipartiteSBM(R_obs,model = "poisson",covariates = c(cov_row,cov_col),estimOptions = list(plot=F,verbosity=0,exploreMax = 10))

model1 = try1[[best_ICL(try1)]]
model2 = try2[[best_ICL(try2)]]
model3 = try3

proba_connect1 = model1$pi[model1$cluster1,model1$cluster2]
proba_connect2 = model2$connectivity_prob
proba_connect3 = 1-exp(-fitted(model3))



ARIL1=ARI(model1$cluster1,Z1_obs)
ARIC1=ARI(model1$cluster2,Z2_obs)

ARIL2=ARI(model2$cluster1,Z1_obs)
ARIC2=ARI(model2$cluster2,Z2_obs)

ARIL3=ARI(model3$memberships$row,Z1_obs)
ARIC3=ARI(model3$memberships$col,Z2_obs)

AUC_LBM  = auc(roc(M_obs[V==0],proba_connect1[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_CoOP = auc(roc(M_obs[V==0],proba_connect2[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_DCSBM = auc(roc(M_obs[V==0],proba_connect3[V==0],
                    direction="<",levels=levels(as.factor(c(0,1)))))
result3[nrow(result3)+1,] = c(ARIL1,ARIC1,ARIL2,ARIC2,ARIL3,ARIC3,AUC_LBM,AUC_CoOP,AUC_DCSBM)

}

```


```{r, warning = FALSE}

df1 = result3[c("ARI_row_LBM","ARI_row_CoOP","ARI_row_DCSBM")]
df1 = melt(df1)
p1 <- ggplot(df1, aes(y=value,fill=variable))+
  geom_boxplot() +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for row clustering")+ labs(y="ARI",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM"))+ guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))

df2 = result3[c("ARI_col_LBM","ARI_col_CoOP","ARI_col_DCSBM")]
df2 = melt(df2)
p2 <- ggplot(df2, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for column clustering")+ labs(y="",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))


grid.arrange(p1,p2,ncol=2)

```

```{r,warning=FALSE}
df3 = result3[c("AUC_LBM","AUC_CoOP","AUC_DCSBM")]

df3_long <- melt(df3)
p3 <- ggplot(df3_long, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("AUC for missing data")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+labs(y="AUC")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))
p3
```

# Global sampling effort is structured in cluster independent from $Z^1$ and $Z^2$

In this situation, the model is the same as usual, but the parameter $G$ depends on an clustering independent from $Z^1$ and $Z^2$ 
```{r}
result4 = data.frame(ARI_row_LBM=numeric(),
                    ARI_col_LBM=numeric(),
                    ARI_row_CoOP = numeric(),
                    ARI_col_CoOP = numeric(),
                    ARI_row_DCSBM = numeric(),
                    ARI_col_DCSBM = numeric(),
                    AUC_LBM = numeric(),
                    AUC_CoOP = numeric(),
                    AUC_DCSBM = numeric()
                   )
```

```{r  simu4 , cache=T, message=FALSE, results='hide'}
for (k in 1:30){

simulation1=simulate_lbm(P,alpha1,alpha2,n1,n2)
M = simulation1$A
Z1 =simulation1$Z
Z2 =simulation1$W

G0 = matrix(runif(16),nrow=4)*50+10
Z1G = sample(1:4,size=n1,replace=T)
Z2G = sample(1:4,size=n2,replace=T)
G0 = G0[Z1G,Z2G]
lambda_i =rbeta(n1,0.3,1.5)
mu_j = rbeta(n2,0.3,1.5)
lambda_i = lambda_i/max(lambda_i)
mu_j = mu_j/max(mu_j)
N0=lambda_i%*%t(mu_j)*G0
N=matrix(rpois(n1*n2,N0),nrow=n1)
R = M*N

obsrow = rowSums(R)>0
obscol = colSums(R)>0
R_obs = R[obsrow,obscol]
M_obs = M[obsrow,obscol]
Z1_obs = Z1[obsrow]
Z2_obs = Z2[obscol]
V = 1*(R_obs>0)

cov_row = lapply(2:nrow(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[k,] = 1
  X
})
cov_col = lapply(2:ncol(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[,k] = 1
  X
})


try1=fit_unsupervised_LBM(V,exploOptions = list(plot=FALSE,verbosity=F))
try2=fit_unsupervised_CoOP_LBM(R_obs,exploOptions = list(plot=F,verbosity=F))
try3 = estimateBipartiteSBM(R_obs,model = "poisson",covariates = c(cov_row,cov_col),estimOptions = list(plot=F,verbosity=0,exploreMax = 10))

model1 = try1[[best_ICL(try1)]]
model2 = try2[[best_ICL(try2)]]
model3 = try3

proba_connect1 = model1$pi[model1$cluster1,model1$cluster2]
proba_connect2 = model2$connectivity_prob
proba_connect3 = 1-exp(-fitted(model3))



ARIL1=ARI(model1$cluster1,Z1_obs)
ARIC1=ARI(model1$cluster2,Z2_obs)

ARIL2=ARI(model2$cluster1,Z1_obs)
ARIC2=ARI(model2$cluster2,Z2_obs)

ARIL3=ARI(model3$memberships$row,Z1_obs)
ARIC3=ARI(model3$memberships$col,Z2_obs)

AUC_LBM  = auc(roc(M_obs[V==0],proba_connect1[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_CoOP = auc(roc(M_obs[V==0],proba_connect2[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_DCSBM = auc(roc(M_obs[V==0],proba_connect3[V==0],
                    direction="<",levels=levels(as.factor(c(0,1)))))
result4[nrow(result4)+1,] = c(ARIL1,ARIC1,ARIL2,ARIC2,ARIL3,ARIC3,AUC_LBM,AUC_CoOP,AUC_DCSBM)

}
```


```{r, warning = FALSE}

df1 = result4[c("ARI_row_LBM","ARI_row_CoOP","ARI_row_DCSBM")]
df1 = melt(df1)
p1 <- ggplot(df1, aes(y=value,fill=variable))+
  geom_boxplot() +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for row clustering")+ labs(y="ARI",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM"))+ guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))

df2 = result4[c("ARI_col_LBM","ARI_col_CoOP","ARI_col_DCSBM")]
df2 = melt(df2)
p2 <- ggplot(df2, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for column clustering")+ labs(y="",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))


grid.arrange(p1,p2,ncol=2)

```

```{r,warning=FALSE}
df3 = result4[c("AUC_LBM","AUC_CoOP","AUC_DCSBM")]

df3_long <- melt(df3)
p3 <- ggplot(df3_long, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("AUC for missing data")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+labs(y="AUC")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))
p3
```





# $\lambda$ and $\mu$ are structured in cluster identical to $Z^1$ and $Z^2$

In this situation, $\lambda$ and $\mu$ are also structured, this simulation is done to see if the structure of the sampling can perturb the estimation of network's structure.

```{r}
result5 = data.frame(ARI_row_LBM=numeric(),
                    ARI_col_LBM=numeric(),
                    ARI_row_CoOP = numeric(),
                    ARI_col_CoOP = numeric(),
                    ARI_row_DCSBM = numeric(),
                    ARI_col_DCSBM = numeric(),
                    AUC_LBM = numeric(),
                    AUC_CoOP = numeric(),
                    AUC_DCSBM = numeric()
                   )
G=20
```

```{r simu5 , cache=T, message=FALSE, results='hide'}
for (k in 1:30){
simulation1=simulate_lbm(P,alpha1,alpha2,n1,n2)
M = simulation1$A
Z1 =simulation1$Z
Z2 =simulation1$W
v1 = c(1,rbeta(2,0.3,1.5))
v2 = c(1,rbeta(2,0.3,1.5))
v1=sample(v1)
v2=sample(v2)
lambda_i =v1[Z1]
mu_j =v2[Z2]
N0=lambda_i%*%t(mu_j)*G
N=matrix(rpois(n1*n2,N0),nrow=n1)
R = M*N

obsrow = rowSums(R)>0
obscol = colSums(R)>0
R_obs = R[obsrow,obscol]
M_obs = M[obsrow,obscol]
Z1_obs = Z1[obsrow]
Z2_obs = Z2[obscol]
V = 1*(R_obs>0)

cov_row = lapply(2:nrow(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[k,] = 1
  X
})
cov_col = lapply(2:ncol(V),function(k){
  X = matrix(0,nrow(V),ncol(V))
  X[,k] = 1
  X
})


try1=fit_unsupervised_LBM(V,exploOptions = list(plot=FALSE,verbosity=F))
try2=fit_unsupervised_CoOP_LBM(R_obs,exploOptions = list(plot=F,verbosity=F))
try3 = estimateBipartiteSBM(R_obs,model = "poisson",covariates = c(cov_row,cov_col),estimOptions = list(plot=F,verbosity=0,exploreMax = 10))

model1 = try1[[best_ICL(try1)]]
model2 = try2[[best_ICL(try2)]]
model3 = try3

proba_connect1 = model1$pi[model1$cluster1,model1$cluster2]
proba_connect2 = model2$connectivity_prob
proba_connect3 = 1-exp(-fitted(model3))



ARIL1=ARI(model1$cluster1,Z1_obs)
ARIC1=ARI(model1$cluster2,Z2_obs)

ARIL2=ARI(model2$cluster1,Z1_obs)
ARIC2=ARI(model2$cluster2,Z2_obs)

ARIL3=ARI(model3$memberships$row,Z1_obs)
ARIC3=ARI(model3$memberships$col,Z2_obs)

AUC_LBM  = auc(roc(M_obs[V==0],proba_connect1[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_CoOP = auc(roc(M_obs[V==0],proba_connect2[V==0],
                   direction="<",levels=levels(as.factor(c(0,1)))))
AUC_DCSBM = auc(roc(M_obs[V==0],proba_connect3[V==0],
                    direction="<",levels=levels(as.factor(c(0,1)))))
result5[nrow(result5)+1,] = c(ARIL1,ARIC1,ARIL2,ARIC2,ARIL3,ARIC3,AUC_LBM,AUC_CoOP,AUC_DCSBM)

}
```


```{r, warning = FALSE}

df1 = result5[c("ARI_row_LBM","ARI_row_CoOP","ARI_row_DCSBM")]
df1 = melt(df1)
p1 <- ggplot(df1, aes(y=value,fill=variable))+
  geom_boxplot() +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for row clustering")+ labs(y="ARI",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM"))+ guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))

df2 = result5[c("ARI_col_LBM","ARI_col_CoOP","ARI_col_DCSBM")]
df2 = melt(df2)
p2 <- ggplot(df2, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(legend.position = "bottom",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("ARI for column clustering")+ labs(y="",x="")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))


grid.arrange(p1,p2,ncol=2)

```

```{r,warning=FALSE}
df3 = result5[c("AUC_LBM","AUC_CoOP","AUC_DCSBM")]

df3_long <- melt(df3)
p3 <- ggplot(df3_long, aes(y=value,fill=variable))+
  geom_boxplot()  +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("AUC for missing data")+scale_fill_discrete(labels = c("LBM","CoOP-LBM","DCSBM")) + guides(fill=guide_legend(title=""))+labs(y="AUC")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ylim(c(0,1))
p3
```








